A Large-scale Study of Polymorphism in R

### 2019-04-02 notebooks/paper_L123_results_section.Rmd

# L <: I <: D
los <- lapply(los, function(lofun) lapply(lofun, logical_int_double_subtype_df))
```

@@

Step 2.2: Top.
```{r}
L0_poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
L0_poly_type_args <- L0_poly_type_args[order(-L0_poly_type_args$count),] # sort by count
L0_poly_type_args$perc <- round(L0_poly_type_args$count/sum(L0_poly_type_args$count) * 100, 2)
```

Step 2.3: Print top 10.
```{r}
format_df_for_print(L0_poly_type_args[1:10,]) %>%
xtable %>% print(include.rownames=F)
```

@@

Step 3.3: Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

@@

```{r}
format_df_for_print(L3_poly_class_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

>>>>

# L <: I <: D
los <- lapply(los, function(lofun) lapply(lofun, function(df) logical_int_double_subtype_df(logical_int_double_subclass_df(df))))

# TODO: error -> ?
los <- lapply(los, function(lofun) lapply(lofun, map_error_to_any))
```

@@

DEBUG: Classes
```{r}
L0_poly_class_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_class_args))
L0_poly_class_args <- L0_poly_class_args[order(-L0_poly_class_args$count),] # sort by count
L0_poly_class_args$perc <- round(L0_poly_class_args$count/sum(L0_poly_class_args$count) * 100, 1)
```
```

Step 2.2: Top.
```{r}
L0_poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
L0_poly_type_args <- L0_poly_type_args[order(-L0_poly_type_args$count),] # sort by count
L0_poly_type_args$perc <- round(L0_poly_type_args$count/sum(L0_poly_type_args$count) * 100, 1)
```

Step 2.3: Print top 10.
```{r}
format_df_for_print(L0_poly_type_args[1:20,]) %>%
xtable %>% print(include.rownames=F)
```

Get the distribution of arguments in the monomorphic case.
```{r}
L0_mono_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_mono_type_args))
L0_mono_type_args <- L0_mono_type_args[order(-L0_mono_type_args$count),] # sort by count
L0_mono_type_args$perc <- round(L0_mono_type_args$count/sum(L0_mono_type_args$count) * 100, 1)

format_df_for_print(L0_mono_type_args[1:20,]) %>%
xtable %>% print(include.rownames=F)
```

@@

Step 3.3: Print top 10.
```{r}
format_df_for_print(poly_type_args[1:20,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

@@

```{r}
format_df_for_print(L3_poly_class_args[1:20,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

### 2019-04-02 paper/main.tex

Figure~\ref{fig:L1argcounts} shows the polymorphicity of argument positions
 in R function.  From there, we build up a picture of the polymorphicity of
 functions as a whole, and the data for this function polymorphism can be
 found in Figure~\ref{fig:L1funcounts}.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 29 18:10:23 2019
\begin{table}[ht]\label{fig:L1argcounts}\centering\begin{tabular}{lrr}  \hline
Type                   & Count & Percentage \\  \hline
  Monomorphic in Type & 845K & 92.46 \\
  Total Seen & 914K & --- \\
   \hline
\end{tabular}
\caption{typeof type system (L0) (arguments)}
\end{table}
% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 29 18:10:23 2019
\begin{table}[ht]
\label{fig:L1funcounts}
\centering
\begin{tabular}{lrr}
  \hline
Type & Count & Percentage \\
  \hline
  Monomorphic in Type & 173K & 80.16 \\
  Total Seen & 216K & --- \\
   \hline
\end{tabular}
\caption{typeof type system (L0) (functions)}
\end{table}

From Figure~\ref{fig:L1argcounts}, we glean that argument positions aren't
very polymorphic in L0.  An argument which is "Monomorphic in Type" is
monomorphic w.r.t. \code{typeof}, in that it was only ever observed to have
one \code{typeof}.  Similarly, an argument is "Monomorphic in Class" if it
is only ever called with one {\tt class}.  As we said earlier, attributes
are a little more complicated, and an argument which is "Monomorphic in
Attribute Pattern" was only ever observed to have one attribute pattern (and
that pattern may itself contain many attributes).

As for the polymorphism of functions as a whole, we glean from
Figure~\ref{fig:L1funcounts} that a sizeable number of functions are
polymorphic.  Functions are said to be polymorphic if at least one of their
arguments or return are polymorphic.  \AT{Say more?}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsL1}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\
  \hline
  Full Monomorphic & 781K & 85.37 \\
  Monomorphic in Type & 834K & 91.23 \\
%  Monomorphic in Class & 827K & 90.42 \\
%  Monomorphic in Attribute Pattern & 825K & 90.27 \\
  Total Seen & 914K & --- \\
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in L1.}
\end{table}

>>>>

Table~\ref{tab:L0argcounts} shows the polymorphicity of argument positions
 in R function.  From there, we build up a picture of the polymorphicity of
 functions as a whole, and the data for this function polymorphism can be
 found in Figure~\ref{tab:L0funcounts}.

\begin{table}[ht]\label{tab:L0argcounts}\centering\begin{tabular}{lrr}  \hline
Type                   & Count & Percentage \\  \hline
  Monomorphic in Type & 845K & 92.46 \\
  Total Seen & 914K & --- \\
   \hline
\end{tabular}
\caption{Argument position polymorphism in L0.}
\end{table}

\begin{table}[ht]
\label{tab:L0funcounts}
\centering
\begin{tabular}{lrr}
  \hline
Type & Count & Percentage \\
  \hline
  Monomorphic in Type & 173K & 80.16 \\
  Total Seen & 216K & --- \\
   \hline
\end{tabular}
\caption{Function polymorphism in L0.}
\end{table}

From Table~\ref{tab:L0argcounts}, we glean that argument positions aren't
very polymorphic in L0.  An argument which is "Monomorphic in Type" is
monomorphic w.r.t. \code{typeof}, in that it was only ever observed to have
one \code{typeof}.  Similarly, an argument is "Monomorphic in Class" if it
is only ever called with one {\tt class}.  As we said earlier, attributes
are a little more complicated, and an argument which is "Monomorphic in
Attribute Pattern" was only ever observed to have one attribute pattern (and
that pattern may itself contain many attributes).

As for the polymorphism of functions as a whole, we glean from
Figure~\ref{tab:L0funcounts} that a sizeable number of functions are
polymorphic.  Functions are said to be polymorphic if at least one of their
arguments or return are polymorphic.  \AT{Say more?}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsL1}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\
  \hline
%  Full Monomorphic & 781K & 85.37 \\
  Monomorphic in Type & 834K & 91.23 \\
%  Monomorphic in Class & 827K & 90.42 \\
%  Monomorphic in Attribute Pattern & 825K & 90.27 \\
  Total Seen & 914K & --- \\
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in L1.}
\end{table}
